---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BSDMR

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of BSDMR is to find DMRs between species by high order methylation profile.

## Installation

You can install the released version of BSDMR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("BSDMR")
```

And the development version from [GitHub](https://github.com/geneprophet/BSDMR) with:

``` r
# install.packages("devtools")
devtools::install_github("geneprophet/BSDMR")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(BSDMR)
## basic example code
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot_infer_profiles(region = 44, obj_prof = human_fit_profiles,obj_mean = human_fit_mean, 
                     obs = human_obj, title = paste0("Gene ID ",human_obj$anno$id[44]))
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!
